Disturbance-aware minimum-time planning strategies for motorsport vehicles with probabilistic safety certificates

### 2025-05-09 intro.tex
[MGa] small mod

In the second one -- the closed-loop covariance-aware planning, we integrate a time-varying LQR feedback policy into the planning process to realistically tame uncertainty growth. First, a nominal time-optimal trajectory is computed under deterministic dynamics. Second, an LQR controller is designed to stabilize that nominal path. Finally, we re-solve the planning problem - together with the feedback gains - so that the closed-loop covariance propagation satisfies tightened constraints via a Lyapunov-based formulation. Together, these two approaches strike a balance between computational simplicity and realistic, feedback-informed robustness, laying the groundwork for safe, high-performance lap-time planning under uncertainty.

>>>>

In the second one -- the closed-loop covariance-aware planning, we integrate a time-varying LQR feedback policy into the planning process to realistically tame uncertainty growth. First, a nominal time-optimal trajectory is computed under deterministic dynamics. Second, an LQR controller is designed to stabilize that nominal path. Finally, we re-solve the planning problem - together with the feedback gains - so that, along this new nominal trajectory, the closed-loop covariance propagation satisfies tightened constraints via a Lyapunov-based formulation. These two approaches offer a balance between computational simplicity and realistic, feedback-informed robustness, laying the groundwork for safe, high-performance lap-time planning under uncertainty in the motorsport context.
